---
title: "Homework2"
output: html_document
---
 
 **Alexis Jorgensen**

**Note** None of the datasets examined in this assignment follow a normal distribution. This violates the assumptions of most of the t-tests performed which may decrease the accuracy of results.

# Scenario 1

a) Ha: The mean catch (in tonnes) has changed between 2009 and 2010

Ho: the mean shrimp catch was the same in 2009 and 2010

```{r}
FishCatch <- read.csv("FishCatch.csv")
names(FishCatch)
attach(FishCatch)

```


b)
```{r}
hist(FishCatch$X2009.catch.tonnes,main = "Shrimp Catch 2009", xlab = "Annual Shrimp Catch (Tonnes)", ylab = "# Communities Surveyed", col="gold")

hist(FishCatch$X2010.catch.tonnes,main = "Shrimp Catch 2010", xlab = "Annual Shrimp Catch (Tonnes)", ylab = "# Communities Surveyed", col="orange", ylim = c(0,4))
```



c) A paired two sample to test should be used to test the hypothesis as there are two mean values to compare. The test is paired because the data was collected at the same lcoations.


d)
```{r}
t.test(X2010.catch.tonnes,X2009.catch.tonnes, paired=T)
```


p << than 0.05 so we reject the null hypothesis that there is no difference between the two groups


e)
```{r}
qt(0.025,13)
```

-2.160369 > -6.3808 so tcrit > tobserved


f) The test indicates that there is a signficant difference in shrimp catch between years

# Scenario 2

```{r}
Site<-c(1,2,3,4,5,6,7,8,9,10)
Ph<-c(18.4,12.9,15.3,18.3,15.6,23.3,16.5,12.3,24.6,16.2)
SitePh<-data.frame(Site,Ph)
SitePh
```


Guideline: 15micrograms/L

a) Ho: The phosphorus levels in the lake are signifcantly different than the guideline

Ha: the phosphorus levels in the lake are not signifcantly different than the guidline


b)
```{r}
hist(SitePh$Ph,main="Phosphorus Levels in Lake Erie", las=1, xlab=expression(paste("Phosphorus Consentration (", mu,"g/L)")), ylab= "# Sample Sites", ylim=c(0,3),col="purple")
```

c) A one-sample t-test should be used to test the hypothesis as it involved comparing the data mean to a specific given value. 

d)
```{r}
shapiro.test(SitePh$Ph)
t.test(SitePh,mu=15)
```


e)
```{r}
qt(0.95,19)
0.3358/2
```
-1.833113 > -2.2909 so tcrit > tobserved. Also p < 0.05

f)The analysis supports the hypothesis that the level of phosphorus in lake Erie is signficantly greater than 15micrograms/L

# Scenario 3

a)Ho: There is no difference in growth rates betweent the fish fed a carniverous vs vegetarian diet
Ha: There is a difference in the growth rate between fsh fed a carniverous and vegetarian diet

b)
```{r}
Carnivor<-c(2.3,1.8,1.9,1.8,2.1,2.3,2.0,2.2,2.2,1.5,1.8,2.1,2.3,2.2,2.3)
Veg<-c(1.6,1.1,0.7,1.0,1.0,0.9,1.2,0.8,0.9,0.6,0.7,0.6,0.8,0.8,1.1)
Diet<-data.frame(Carnivor,Veg)

hist(Carnivor,main="Growth rate of Farmed Salmon fed a Carniverous Diet",xlab="Growth rate (%/day)", ylab="# Trials", col="darkred")

hist(Veg,main="Growth rate of Farmed Salmon fed a Vegetarian Diet",xlab="Growth rate (%/day)", ylab="# Trials", col="darkgreen")

```


c) A Two sample t-test should be used as we are comparing two populations with different means, but they are within the same enviornment otherwise (same farm)

d) 
```{r}
t.test(Veg, Carnivor)
```

e)
```{r}
qt(0.025,14)
```

-2.144787 > -15.162 so tcrit > tobserved, and p << 0.05

f)There is a significant difference in the growth rates between fish fed carniverous and vegetarian diets

# Scenario 4

a)Ha: Species trophic level and the impacts of PCB exposure are not independant
Ho: Species trophic level and the impacts of PCB exposure are independant

b)
```{r}
PCB<-read.csv("PCB.csv")
PCB
```

c)A chi-squared test should be used for this analysis

d)
```{r}
chisq.test(PCB[1:2,2:4])
```

e)
```{r}
qchisq(0.95,2)
```
chisq observed >> chisq crit and p << 0.05

f) The null hypothesis that PCB impacts are indepedant of trophic level can be rejected.
